---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lantern

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/topepo/lantern/branch/master/graph/badge.svg)](https://codecov.io/gh/topepo/lantern?branch=master)
<!-- badges: end -->

lantern packages several modeling functions that use the torch package.  

## Installation

You can install the released version of lantern from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("lantern")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("topepo/lantern")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(lantern)
## basic example code
```

## Code of Conduct
  
Please note that the lantern project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

