---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lantern

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/topepo/lantern/branch/master/graph/badge.svg)](https://codecov.io/gh/topepo/lantern?branch=master)
<!-- badges: end -->

`lantern` packages several basic modeling functions that use the `torch` package.  

## Installation

You can install the released version of lantern from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("lantern")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("topepo/lantern")
```
## Example

`lantern` has formula, x/y, and recipe user interfaces for each function. For example:

```{r load, include = FALSE}
library(lantern)
library(yardstick)
library(recipes)
```
```{r class-fit-form}
library(lantern)
library(recipes)
library(yardstick)

data(bivariate, package = "modeldata")
set.seed(20)
nn_log_biv <- lantern_mlp(Class ~ log(A) + log(B), data = bivariate_train, 
                          epochs = 150, hidden_units = 3, batch_size = 64)

# We use the tidymodels semantics to always return a tibble when predicting
predict(nn_log_biv, bivariate_test, type = "prob") %>% 
  bind_cols(bivariate_test) %>% 
  roc_auc(Class, .pred_One)
```

A recipe can also be used if the data require some sort of preprocessing (e.g., indicator variables, transformations, or standardization): 

```{r class-fit-rec}
library(recipes)

rec <- 
  recipe(Class ~ ., data = bivariate_train) %>%  
  step_YeoJohnson(all_predictors()) %>% 
  step_normalize(all_predictors())

set.seed(20)
nn_rec_biv <- lantern_mlp(rec, data = bivariate_train, 
                          epochs = 150, hidden_units = 3, batch_size = 64)

# A little better
predict(nn_rec_biv, bivariate_test, type = "prob") %>% 
  bind_cols(bivariate_test) %>% 
  roc_auc(Class, .pred_One)
```

## Code of Conduct
  
Please note that the lantern project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

