---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# brulee

<!-- badges: start -->
[![R-CMD-check](https://github.com/tidymodels/brulee/workflows/R-CMD-check/badge.svg)](https://github.com/tidymodels/brulee/actions)
[![Codecov test coverage](https://codecov.io/gh/tidymodels/brulee/branch/main/graph/badge.svg)](https://app.codecov.io/gh/tidymodels/brulee?branch=main)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html)
<!-- badges: end -->

The R `brulee` package contains several basic modeling functions that use the `torch` package (and is unrelated to the python script).  

The package is currently experimental; the user interface and other details may change before release. 

## Installation

You can install the released version of brulee from [CRAN](https://CRAN.R-project.org) with:

``` r
# not yet!
# install.packages("brulee")
```

And the development version from [GitHub](https://github.com/tidymodels/brulee) with:

``` r
# install.packages("devtools")
devtools::install_github("tidymodels/brulee")
```
## Example

`brulee` has formula, x/y, and recipe user interfaces for each function. For example:

```{r load, include = FALSE}
library(brulee)
library(yardstick)
library(recipes)
```
```{r class-fit-form}
library(brulee)
library(recipes)
library(yardstick)

data(bivariate, package = "modeldata")
set.seed(20)
nn_log_biv <- brulee_mlp(Class ~ log(A) + log(B), data = bivariate_train, 
                         epochs = 150, hidden_units = 3, batch_size = 64)

# We use the tidymodels semantics to always return a tibble when predicting
predict(nn_log_biv, bivariate_test, type = "prob") %>% 
  bind_cols(bivariate_test) %>% 
  roc_auc(Class, .pred_One)
```

A recipe can also be used if the data require some sort of preprocessing (e.g., indicator variables, transformations, or standardization): 

```{r class-fit-rec}
library(recipes)

rec <- 
  recipe(Class ~ ., data = bivariate_train) %>%  
  step_YeoJohnson(all_predictors()) %>% 
  step_normalize(all_predictors())

set.seed(20)
nn_rec_biv <- brulee_mlp(rec, data = bivariate_train, 
                         epochs = 150, hidden_units = 3, batch_size = 64)

# A little better
predict(nn_rec_biv, bivariate_test, type = "prob") %>% 
  bind_cols(bivariate_test) %>% 
  roc_auc(Class, .pred_One)
```

## Code of Conduct
  
Please note that the brulee project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

